### 2019-12-06 reports/media/tightly_acc.tex
rotate FUs

    % busses
    \draw[ultra thick] (0, 1) -- (9, 1);
    \draw[ultra thick] (0, -5.5) -- (9, -5.5);
    \draw[ultra thick] (1, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (1, -0.5);
    \draw[ultra thick] (5, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (5, -0.75);
    \draw[ultra thick] (8.25, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (8.25, -1.75);

    \draw[ultra thick] (1, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
    \draw[ultra thick] (5, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
    \draw[ultra thick] (8.25, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);

@@

    % functional units
    \begin{scope}[name=fu, local bounding box=fubb, shift={(4, 0)}]
      \node at (0.25, 0.25) [anchor=south] {FUs};
      \begin{scope}[shift={(0.25, 0.15)}]
      \draw [fill=white, thick] (0, 0) -- (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- (0, -5) -- (1.5, -3.5) -- (1.5, -1.5) -- cycle;
      \end{scope}
      \begin{scope}
        \draw [fill=white, thick] (0, 0) -- node [coord] (alua) {} (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- node [coord] (alub) {}
        (0, -5) -- (1.5, -3.5) -- node [coord] (alux) {} (1.5, -1.5) -- cycle;
      \end{scope}
    \end{scope}

>>>>

    % busses
    \draw[ultra thick] (0, 1) -- (9, 1);
    \draw[ultra thick] (0, -5.5) -- (9, -5.5);
    \draw[ultra thick] (1, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (1, -0.5);
    \draw[ultra thick] (3.75, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -3.5);
    \draw[ultra thick] (6, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, -3.5);
    \draw[ultra thick] (8.25, 1) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- (8.25, -1.75);

    \draw[ultra thick] (1, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2);
    \draw[ultra thick] (4.65, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);
    \draw[ultra thick] (8.25, -5.5) node [circle, minimum size=4pt, fill, inner sep=0pt] {} -- ++(0, 2.5);

@@

    % functional units
    \begin{scope}[name=fu, local bounding box=fubb, shift={(6.5, -2)}]
      \node at (-1.5, 0.25) [anchor=south] {FUs};
      \begin{scope}[shift={(0.25, 0.15)}, rotate=-90, scale=0.75]
        \draw [fill=white, thick] (0, 0) -- (0, -1.75) -- (0.75, -2.5) -- (0, -3.25) -- (0, -5) -- (1.5, -3.5) -- (1.5, -1.5)
        -- cycle;
      \end{scope}
      \begin{scope}[rotate=-90, scale=0.75]
        \draw [fill=white, thick] (0, 0) -- node [coord] (alua) {} (0, -1.75) -- (0.75, -2.5) -- (0, -3.25)
        -- node [coord] (alub) {}
        (0, -5) -- (1.5, -3.5) -- node [coord] (alux) {} (1.5, -1.5) -- cycle;
      \end{scope}
    \end{scope}
